\documentclass[10pt, a4paper, twoside]{exam}
\usepackage[left=0.5in, top=0.5in, total={7.27in, 10.3in}]{geometry}

\begin{document}
	\begin{questions}
		\question Draw Stress-strain graph for a metallic solid and show
    
        \begin{parts}
            \setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
            \setlength{\parsep}{0pt}
            \part elastic limit, 
            \part region of plasticity
            \part point of ultimate tensile strength and
            \part Fracture point on the graph.
        \end{parts}
        
        \question Write the number of significant digits in the following
    
        \begin{parts}
            \setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
            \setlength{\parsep}{0pt}
            \part 1001
            \part 100.1
            \part 0.001001
            \part 100.10
        \end{parts}
        
        \question State the number of significant figures in the following
    
        \begin{parts}
            \setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
            \setlength{\parsep}{0pt}
            \part $0.007 \; m^2$
            \part $2.64 \times 10^{24} \; m^2$ 
            \part $ 0.2370 \; g/cm^{-2}$
        \end{parts}
        
        \question Round the following numbers to 2 significant digits
    
        \begin{parts}
            \setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
            \setlength{\parsep}{0pt}
            \part $3472$
            \part $2.55$ 
            \part $84.16$
            \part $28.5$
        \end{parts}
        
        \question Write down the number of significant figures in the following:
    
        \begin{parts}
            \setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
            \setlength{\parsep}{0pt}
            \part $6428$
            \part $62.00 \; m$ 
            \part $0.00628 \; cm$
            \part $1200 \; N$
        \end{parts}
        
        \question The mass of a box measured by a grocer's balance is $2.300 \; kg$. Two gold pieces of masses $20.15 \; g$ and $20.17 \; g$ are added to the box. What is 
        
        \begin{parts}
            \setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
            \setlength{\parsep}{0pt}
            \part the total mass of the box,
            \part the difference in the masses of the pieces to correct significant figures?
        \end{parts}
        
        \question Length, breadth and thickness of a rectangular slab are $4.234 \; m, 1.005 \; m $ and $ 2.01 \; m$ respectively. Find volume of the slab to correct significant figures.
        
        \question A physical quantity $\rho$ is related to four variables $\alpha, \; \beta, \; \gamma$ and $\eta$ as: \[ \rho = \frac{\alpha^3\beta^2}{\eta\sqrt{\gamma}} \] The percentage errors of measurements in $\alpha, \; \beta, \; \gamma$ and $\eta$ are $1\%,\; 3\%, \;4\%$ and $2\%$ respectively. Find the percentage error in $\rho$.
        
        \question The period of oscillation of a simple pendulum is $T=2\pi\sqrt{L⁄g}$. Measured value of $L$ is $20.0\; cm$ known to $1\; mm$ accuracy and time for 100 oscillations of the pendulum is found to be 90$s$ using a wrist watch of $1s$ resolution. What is the accuracy in the determination of $g$?
        
		\question Find the percentage error in specific resistance given by \[\rho = \frac{\pi r^{2}R}{l}\] where $r$ is the radius having value $(0.2 \pm 0.02) \;cm$, $R$ is the resistance of $(60 \pm 2) \;ohm$ and $l$ is the length of $(150 \pm 0.1)\; cm$.      
		
		\question The resistance \[ R=\frac{V}{I}\] where $V = (100 \pm 5.0) \;V$ and $I = (10 \pm 0.2) \;A$. Find the percentage error in $R$.
		
		\question A thin wire has length of $21.7 \;cm$ and radius $0.46 \;mm$. Calculate the volume of the wire to correct significant figures.
 		
 		\question A cube has a side of length $2.342 \;m$. Find volume and surface area in correct significant figures.
 		
 		\question Add $6.75 \times 10 \;cm^{3}$ to $4.52 \times 10 \;cm^{2}$ with regard to significant figures.
        
        \question The temperature of two bodies measured by a thermometer are $(20 \pm 0.5)^{\circ}C$ and $(50 \pm 0.5)^{\circ}C$. Calculate the temperature difference with error limits.
        
        \question The radius of a sphere is measured to be $(2.1 \pm 0.5) \;cm$. Calculate its surface area with error limits.
        
        \question Find density when a mass of $9.23 \;kg$ occupies a volume of $1.1 \; m^3$. Take care of significant figures.
	\end{questions}
\end{document}